Real-time resolution of short-read assembly graph using ONT long reads

### 2020-08-12 plos_latex_edit.tex
fake motivation

Sequencing technology has reached a level of maturity which allows the decoding of virtually any piece of genetic material which  can be obtained. 
%This provides the potential use of DNA sequencing into a wide range of applications in medical 
%and scientific research. 
However, the time from sample to result remains a barrier to adoption of sequencing technology into time critical applications such as infectious disease diagnostics or clinical decision making. 
While there exists real-time sequencing technology such as Oxford Nanopore Technologies (ONT), algorithms for streaming analyses of such real-time data are still in their infancy. Effective streaming methodology will help bridge the gap between potential and practical use. 
\addnew{In addition, the release of Read Until API enables direct control to the actual molecular reading process which has paved the way for customized selective and/or enrichment sequencing on ONT platforms. To function properly, methods using this protocol must implement rapid-responsed operations on the streaming data, for example in ReadFish~\cite{Payne2020}.}

>>>>

Sequencing technology has reached a level of maturity which allows the decoding of virtually any piece of genetic material which  can be obtained. 
%This provides the potential use of DNA sequencing into a wide range of applications in medical 
%and scientific research. 
However, the time from sample to result remains a barrier to adoption of sequencing technology into time critical applications such as infectious disease diagnostics or clinical decision making. 
While there exists real-time sequencing technology such as Oxford Nanopore Technologies (ONT), algorithms for streaming analyses of such real-time data are still in their infancy. Effective streaming methodology will help bridge the gap between potential and practical use. 
\addnew{In addition, the release of Read Until API enables direct control to the actual molecular reading process which has paved the way for customized targeted sequencing on ONT platforms. To function properly, such methods must implement a real-time ultrafast operation on the streaming data, \EG{} in ReadFish~\cite{Payne2020}. Up until now, there is a shortage of similar tools that can utilize this distinctive feature.}
